\section*{Part A: Hall Sensors}
\addcontentsline{toc}{section}{Part A: Hall Sensors}

\paragraph{Task 1 a) Best intrinsic semiconductor.}
The current-related sensitivity of a Hall plate is $S_I = rG/(n\,q\,t)$ and the voltage-related
sensitivity is $S_V = \mu\,rG/\LWeff$. For an intrinsic material $n=n_i$, so a good Hall sensor
wants a \emph{low} intrinsic carrier concentration and a \emph{high} mobility. Reading Table~1:

\begin{center}\small
\begin{tabular}{lccc}
\toprule
 & Si & GaAs & Ge \\
\midrule
$n_i$ [\si{\per\cubic\cm}] & $1.5\times10^{10}$ & $\bm{1.8\times10^{6}}$ & $2.4\times10^{13}$ \\
$\mu_n$ [\si{\square\cm\per\volt\per\second}] & 1350 & \textbf{8500} & 3900 \\
\bottomrule
\end{tabular}
\end{center}

GaAs wins on \emph{both} counts: its intrinsic concentration is four orders of magnitude below Si
(boosting $S_I\propto 1/n_i$) and its electron mobility is the highest of the three (boosting
$S_V\propto\mu$). Its wide bandgap (\SI{1.42}{eV}) also keeps thermally generated carriers low, so
the response stays stable with temperature. \textbf{GaAs is the most suitable.}

\paragraph{Task 1 b) Parameter linking $S_I$ and $S_V$.}
Since $V=I\!\cdot\!R$, the two sensitivities are tied through the \textbf{device resistance $R$}:
\[
S_V=\frac{S}{V}=\frac{S}{I R}=\frac{S_I}{R},\qquad R=R_\square\LWeff .
\]
$R$ matters in its own right because it fixes the bias power $P=V^2/R=I^2R$ (hence self-heating) and
the thermal-noise floor $\overline{u_n^2}=4k_BTR\,\Delta f$. Designing only for sensitivity while
ignoring $R$ can push the device into excessive power dissipation or poor SNR.

\paragraph{Task 1 c) Figure of merit for integrated devices.}
An integrated Hall device runs from a fixed supply \emph{voltage} and a limited power budget, so the
\textbf{voltage-related sensitivity $S_V$} (\si{\volt\per\volt\per\tesla}) is the meaningful figure of
merit, since it is the sensitivity per unit bias and ultimately sets the achievable SNR-per-power,
$\mathrm{SNR}_P\propto \mu\,rG/\LWeff$.

\paragraph{Task 1 d) GaN Hall devices.}
For the Gen~2 device $S_I=\SI{90}{\volt\per\ampere\per\tesla}$, $S_V=\SI{57}{\milli\volt\per\volt\per\tesla}$,
$R_\square=\SI{430}{\ohm}/\square$, with $r=1$.

\textbf{(i)} From $S_V=S_I/\big(R_\square\LWeff\big)$,
\[
\LWeff=\frac{S_I}{S_V\,R_\square}=\frac{90}{0.057\times430}=\mathbf{3.67}.
\]
The geometry factor follows from
\[
G\approx\frac{\LWeff^{2}}{\sqrt{\LWeff^{4}+\tfrac12\LWeff^{2}+4}}
=\frac{3.67^{2}}{\sqrt{3.67^{4}+\tfrac12\,3.67^{2}+4}}=\mathbf{0.97}.
\]
($G$ is close to unity, as expected for the relatively large $L/W$ of a cross/Greek-cross plate.)

\textbf{(ii)} Gen~3 shares Gen~2's geometry, so $\LWeff=3.67$ and $G=0.97$ carry over. With
$S_I=34$, $S_V=\SI{34}{\milli\volt\per\volt\per\tesla}$,
\[
R_{\square,\mathrm{Gen3}}=\frac{S_I}{S_V\LWeff}=\frac{34}{0.034\times3.67}=\mathbf{272\ \si{\ohm}/\square}.
\]

\textbf{(iii)} Sheet carrier density from $S_I=rG/(n_s q)$ and mobility from $S_V=\mu rG/\LWeff$:
\[
n_s=\frac{rG}{S_I\,q},\qquad \mu=\frac{S_V\LWeff}{rG}.
\]

\begin{center}\small
\begin{tabular}{lccc}
\toprule
 & $n_s=n\!\cdot\!t$ [\si{\per\square\cm}] & $\mu$ [\si{\square\cm\per\volt\per\second}] & cross-check $\mu=1/(R_\square q n_s)$ \\
\midrule
Gen~2 & $6.74\times10^{12}$ & $2154$ & \SI{2154}{} \checkmark\\
Gen~3 & $1.78\times10^{13}$ & $1285$ & \SI{1285}{} \checkmark\\
\bottomrule
\end{tabular}
\end{center}

Gen~3's InAlN barrier gives a roughly $2.6\times$ higher 2DEG density but a lower mobility, the
usual density/mobility trade-off in nitride heterostructures.

\textbf{(iv) Additional: silicon comparison} ($\LWeff=\sqrt2$, so
$G=2/\sqrt{4+1+4}=2/3=0.67$; $S_I=300$, $S_V=\SI{60}{\milli\volt\per\volt\per\tesla}$):
\[
R_{\square,\mathrm{Si}}=\frac{300}{0.060\sqrt2}=\mathbf{3536\ \si{\ohm}/\square},\qquad
n_s=\frac{0.67}{300\,q}=1.39\times10^{12}\,\si{\per\square\cm},
\]
\[
\mu_{\mathrm{Si}}=\frac{0.060\sqrt2}{0.67}=\mathbf{1273\ \si{\square\cm\per\volt\per\second}}.
\]
The Si plate has $\sim$\,8$\times$ the sheet resistance of GaN Gen~2 and only $\sim$\,60\% of its
mobility. GaN therefore delivers both a lower $R_\square$ (more current at fixed power) and a higher
mobility, which is exactly why it makes the better integrated Hall material.
